\documentclass[11pt]{ruthesis}


% The page number in Rutgers thesis format is so high up in the
% page that normal printers can not print it out! The following is to
% lower page numbers down a bit, so we can see them in a draft
% version to the committee members. Do NOT use this change in the
% FINAL version to be submitted to the Graduate School.
%\addtolength{\topmargin}{0.3cm}


\usepackage[utf8]{inputenc}	% UTF-8
\usepackage[T1]{fontenc}	% Improve umlaut support
\usepackage{textcomp}		% https://tex.stackexchange.com/questions/49610/use-biblatex-and-utf8
\usepackage{ae}				% German Sharp S
\usepackage{lmodern}
\usepackage[pdftex,bookmarks=true,bookmarksopenlevel=1,colorlinks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{microtype}
\usepackage{float}
\usepackage{rotating}
\usepackage{comment} 
\usepackage{graphicx}
%\usepackage[numbers]{natbib}
\usepackage{slashed}
\usepackage{lmodern}
\usepackage{mathrsfs}
\usepackage{nextpage}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{ifthen}
\usepackage{url}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{savesym}
\usepackage{braket}
\usepackage{subcaption}
\usepackage{units}
\usepackage[backend=bibtex,sorting=none]{biblatex}
\bibliography{thesis.bib}

\newcommand{\equates}{\mathrel{\widehat{=}}}
\providecommand{\fixme}[1]{{\sffamily{\bfseries{}FIXME:} #1}}
\newcommand{\ptRatio}{\ensuremath{\pt^\text{ratio}}\xspace}
\newcommand{\ptRel}{\ensuremath{\pt^\text{rel}}\xspace}
\newcommand{\relIso}{\ensuremath{I_\text{rel}}\xspace}
\newcommand{\miniIso}{\ensuremath{I_\text{mini}}\xspace}
\newcommand{\multiIso}{\ensuremath{I_\text{multi}}\xspace}
\newcommand\hairspace{\kern .08333em }

\pdfpkresolution=2400 % needed for \dlsh and \drsh

\special{papersize=8.5in,11in} %***for A4-default configurations on servers

% Include defined symbols
\input{pennames-pazo.sty}
\input{ptdr-definitions.sty}
\input{user-definitions.sty}


% Begin document
\begin{document}


% Begin title page

\phd 

\title{Search for Type-III Seesaw Heavy Fermions with Multilepton Final States using \fullLumi of \boldmath$\sqrt{\lowercase{s}} = 13\,\TeV$ proton--proton Collision Data}

% Your name must exactly match what is on your transcript
\author{Peter Thomassen}

\program{Physics and Astronomy}

\director{Dr. Sunil Somalwar}

% Physics has five committee members, including your advisor and one member external to the department
% Side note: your external member must be approved by the GSNB - send the dept. grad director a copy of their CV to do that
\approvals{5}

% This is the month you will be awarded the degree, so one of January, May, or October
\submissionmonth{May} 

\submissionyear{2016}

% Begin beforepreface

\copyrightpage % ruthesis.cls boolean to turn copyright on and must be called before \beforepreface is called

% Page ii is the abstract - Must not exceed 2,450 characters and 350 words.
% The abstract should be relatively jargon-free but still contain any relevant keywords for search engines.
\abstract{
A search for type-III seesaw signal in events with three or more electrons or muons is presented. The data sample corresponds to \fullLumi\ of integrated luminosity in $pp$ collisions at $\sqrt{s} = 13\,\TeV$ collected by the CMS experiment at the LHC. Since the signal populates channels with at least three leptons and diverse kinematic properties, the data is binned in exclusive channels. The primary selection is based on the number of leptons and the invariant mass of opposite-sign dilepton systems which helps discriminate the signal against the Standard Model background. The final optimization for the type-III seesaw signal is based on the sum of leptonic transerve momenta and missing transverse energy. Control samples in data are used to check the robustness of background evaluation techniques and to minimize the reliance on simulation. The observations are consistent with expectations from Standard Model processes. The results are used to exclude heavy fermions of the type-III seesaw model with masses below 430\,\GeV.}


\beforepreface


% Begin afterpreface

\acknowledgements{
Many individuals and institutions have supported me during my Ph.\,D. studies and thesis writing. I would like to express my graditude especially to my supervisor Prof.~Sunil Somalwar whose advice and guidance were extremely valuable, and to the members of our research groups, especially Dr.~Richard Gray, Dr.~Matt Walker, and Dr.~Halil Saka, as well as to my fellow graduate students Sanjay Arora, Christian Contreras-Campaña, Emmanuel Contreras-Campaña, Maximilian Heindl, Shruti Panwalkar, Patrick Zywicki for their helpful discussions, input, and distractions. Special thanks go to Prof.~Scott Thomas for his guidance on theoretical matters, and to Ezio Torassa and Andrea Gozzelino for the collaboration on the seesaw model, and to my dear fellow student Elliot ``Tote'' Hughes.

My involvement with Rutgers University started initially with an exchange organized by Würzburg University. Financial support for the exchange was provided by the German Academic Exchange Service (DAAD). Further funds, for travel purposes as well as generally, came from several scholarships of the Foundation of German Business (Stiftung der Deutschen Wirtschaft, sdw), COLA support from the National Science Foundation (NSF), as well as from Rutgers University and Prof.~Somalwar's NSF grant.

This thesis contains material from previous publications of the author \cite{Thomassen2012,CMS-PAS-EXO-16-002}.
}


%\dedication{
%\begin{center}
%\begin{flushleft}
%\end{flushleft}
%\em{
%I dedicate this dissertation to Emmanuel to whom
%this thesis would not have been possible.}
%\end{center}
%}


\tablespage % ruthesis.cls boolean to turn list of tables on and must be called before \afterpreface is called
\figurespage % ruthesis.cls boolean to turn list of tables on and must be called before \afterpreface is called

\afterpreface

\input{Introduction/Introduction}
\input{Theory/Theory}
\input{Detector/Detector}
\input{Samples/Samples}
\input{Selection/Selection}
\input{Strategy/Strategy}
\input{Background/Background}
\input{Systematics/Systematics}
\input{Results/Results}
\input{Summary/Summary}

\clearpage

%%%%%%%%%%%%%%%%%% Appendix %%%%%%%%%%%%%%%%%%%%
\appendix
\input{Appendix/Appendix}

\clearpage

\addcontentsline{toc}{chapter}{Bibliography}
\begin{singlespace}
%\bibliographystyle{ieeetr}
\printbibliography
\end{singlespace}

%%%%%%%%%%%%%%%%%% End of thesis %%%%%%%%%%%%%%%%%%
%\pagestyle{empty} % Using this removes last page number of the bibliography for unknown reasons

\end{document}
